\def\IsDraft{} % Uncomment for the draft version

\documentclass[11pt]{article}
\usepackage{amsfonts,amsmath,amssymb,boxedminipage,color,url,fullpage,nccmath,amsthm}


\usepackage{color}

\definecolor{weborange}{rgb}{.8,.3,.3}
\definecolor{webblue}{rgb}{0,0,.8}
\definecolor{internallinkcolor}{rgb}{0,.5,0}
\definecolor{externallinkcolor}{rgb}{0,0,.5}


% pageanchor=false solves the warning "pdfTeX warning (ext4): destination with the same identifier (name{page.}) has been already used, duplicate ignored"
\usepackage[pageanchor=false,
colorlinks=true,
urlcolor=externallinkcolor,
linkcolor=internallinkcolor,
filecolor=externallinkcolor,
citecolor=internallinkcolor,
pdfstartview=FitH]{hyperref}

%\usepackage[pagebackref,
%hyperfootnotes=false,
%colorlinks=true,
%urlcolor=externallinkcolor,
%linkcolor=internallinkcolor,
%filecolor=externallinkcolor,
%citecolor=internallinkcolor,
%breaklinks=true,
%pdfstartview=FitH,
%pdfpagelayout=OneColumn]{hyperref}



\usepackage{enumerate,paralist}
\usepackage[numbers]{natbib} % \citet{foo} -> Foo et al. [5]
\usepackage[labelfont=bf]{caption}
\usepackage{aliascnt}
\usepackage{cleveref}
\usepackage{xspace}

\usepackage{relsize}
\usepackage{graphics}
\usepackage[usestackEOL]{stackengine}

%\usepackage{lmodern}% to remove LaTeX font warnings (Using lmodern removes this restriction by allowing font sizes at arbitrary sizes)
\usepackage[T1]{fontenc}

\input{macros}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\inote{\Inote}
\def\rnote{\Rnote}
\def\mnote{\Mnote}
\def\nnote{\Nnote}
\newcommand{\Inote}[1]{\authnote{Iftach}{#1}}
\newcommand{\Mnote}[1]{\authnote{Matan}{#1}}
\newcommand{\Rnote}[1]{\authnote{Ran}{#1}}
\newcommand{\Nnote}[1]{\authnote{Nikos}{#1}}

\newcommand{\iadded}[1]{\added{Iftach}{#1}}
\newcommand{\radded}[1]{\added{Ran}{#1}}
\newcommand{\madded}[1]{\added{Matan}{#1}}
\newcommand{\nadded}[1]{\added{Nikos}{#1}}

\newcommand{\ichanged}[2]{\changed{Iftach}{#1}{#2}}
\newcommand{\rchanged}[2]{\changed{Ran}{#1}{#2}}
\newcommand{\mchanged}[2]{\changed{Matan}{#1}{#2}}
\newcommand{\nchanged}[2]{\changed{Nikos}{#1}{#2}}

\newcommand{\ideleted}[1]{\deleted{Iftach}{#1}}
\newcommand{\rdeleted}[1]{\deleted{Ran}{#1}}
\newcommand{\mdeleted}[1]{\deleted{Matan}{#1}}
\newcommand{\ndeleted}[1]{\deleted{Nikos}{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\newcounter{fnnumber}

\newcommand{\adaptive}{{\MathAlgX{adaptive}\xspace}}
\newcommand{\nonadaptive}{{\MathAlgX{non\mhyphen adaptive}\xspace}}

\newcommand{\BA}{\MathAlgX{BA}}
\newcommand{\Agr}{\MathAlgX{agreement}}
\newcommand{\Vld}{\MathAlgX{validity}}
\renewcommand{\Halt}{\MathAlgX{halting}}


\newcommand{\bls}{\cB_{\ell,\sigma}}

\renewcommand{\o}{b}
\newcommand{\oo}{\overline{\o}}

\newcommand{\omin}{\set{\o,\bot}}
\newcommand{\oomin}{\set{\oo,\bot}}
\newcommand{\vz}{\vv_0}
\newcommand{\vo}{\vv_1}
\newcommand{\oP}{{\overline{\cP}}}
\newcommand{\bns}{\mathbf{D}_{n,\sigma}}
\newcommand{\bne}{\cB_{n,\eps}}
\newcommand{\err}{\mathsf{err}}
\newcommand{\fnk}{\floor{(n-k)/2}}
\newcommand{\cnk}{\ceil{(n-k)/2}}
\newcommand{\fnt}{\floor{(n-t)/2}}
\newcommand{\cnt}{\ceil{(n-t)/2}}

\newcommand{\mon}{\set{\bot^n}}

\newcommand{\FirstErr}{2^{t-n}}

\title{On the Round Complexity of Randomized Byzantine Agreement
\Draft{\\{\small \sc Working Draft: Please Do Not Distribute}}
}

\author{Ran Cohen\thanks{Boston University and Northeastern University. E-mail: \texttt{rancohen@ccs.neu.edu}. Research supported by the Northeastern University Cybersecurity and Privacy Institute Post-doctoral fellowship, IARPA under award 2019-19020700009 (ACHILLES), NSF grant TWC-1664445, NSF grant 1422965, and by the NSF MACS project. Some of this work was done while the author was a post-doc at Tel Aviv University, supported by ERC starting grant 638121.}
\and Iftach Haitner\thanks{School of Computer Science, Tel Aviv University. E-mail: \texttt{iftachh@cs.tau.ac.il}. Member of the Check Point Institute for Information Security.}~\footnotemark[5] %
\and Nikolaos Makriyannis\thanks{Department of Computer Science, Technion. E-mail: \texttt{n.makriyannis@gmail.com}. Research supported by ERC advanced grant 742754.}~\footnotemark[5]
\and Matan Orland\thanks{School of Computer Science, Tel Aviv University. E-mail: \texttt{matanorland@mail.tau.ac.il}.}
\footnote{Research supported by ERC starting grant 638121.}
\and Alex Samorodnitsky\thanks{School of Engineering and Computer Science, The Hebrew University of Jerusalem.\newline{} E-mail: \texttt{salex@cs.huji.ac.il}. Research partially supported by ISF grant 1724/15.}
}

\begin{document}

\sloppy
\maketitle
\begin{abstract}
We prove lower bounds on the round complexity of \emph{randomized} Byzantine agreement (BA) protocols,
bounding the halting probability of such protocols after one and two rounds. In particular, we prove that:

\begin{enumerate}
\item BA protocols resilient against $n/3$ [\resp $n/4$] corruptions terminate (under attack) at the end of the first round with probability at most $o(1)$ [\resp $1/2+ o(1)$].

\item BA protocols resilient against $n/4$ corruptions terminate at the end of the second round with probability at most $1-\Theta(1)$.

\item For a large class of protocols (including all BA protocols used in practice) and under a plausible combinatorial conjecture, BA protocols resilient against $n/3$ [\resp $n/4$] corruptions terminate at the end of the second round with probability at most $o(1)$ [\resp $1/2 + o(1)$].
\end{enumerate}
The above bounds hold even when the parties use a trusted setup phase, \eg a public-key infrastructure (PKI).

The third bound essentially matches the recent protocol of \citeauthor{Micali17} (ITCS'17) that tolerates up to $n/3$ corruptions and terminates at the end of the third round with constant probability.
\end{abstract}

\vfill
\noindent\textbf{Keywords: Byzantine agreement; lower bound; round complexity.}

\Tableofcontents

\input{Introduction}

\input{Technique}

\input{OurResults}
\input{Isoperimetric}
\input{FirstRound}
\input{SecondRound}

\paragraph{Acknowledgements.}
We would like to thank Rotem Oshman, Juan Garay, Ehud Friedgut, and Elchanan Mossel for very helpful discussions.

\bibliographystyle{abbrvnat}
\bibliography{crypto}

\appendix
\input{LocallyConsistentToMalicious}

\end{document}

