%\newcommand{\bls}{{\binom{[\ell]}{\floor{\sigma \ell}}}}


\subsubsection{The Combinatorial Conjecture}\label{sec:CombinatorialConjectures}


\Inote{motivate the conjecture}
\begin{notation}
For $\vx\in \sel$ and $\cS \subseteq [\ell]$, define  $\Del{\vx}{\cS} \in \sbl$ by $
\Del{\vx}{\cS}_i=
\begin{cases}
\bot, & i\in \cs,\\
x_i, & \text{otherwise}.
\end{cases}
$.% Let $\Dels{x}{\cS} = \set{x} \cup \set{\Del{x}{\cS}}$.
\end{notation}
	

Recall that  $\bls$ is the distribution induced on the subset of $[n]$ by taking each element independently with probability $\sigma$.	
\begin{conjecture}\label{conj:1}
For any $\sigma,\lambda, \mu>0$, there exists $q \in \poly$ such that the following holds.  Let  $\Sigma$ be a finite alphabet and let $\cA_0,\cA_1 \subset \sbl$  be  two disjoint sets such that %for both 

\begin{align*}%\label{eq:1}
\ppr{\cS \gets \bls}{\forall b\in \zo \colon \ppr{\vr\gets \sel}{\vr, \Del{\vr}{\cS} \in \cA_b} \ge \lambda} \ge \mu.
\end{align*}
		
Then,
\begin{align*}%\label{eq:2}
\ppr{\vr\gets \sel,\cS \gets \bls}{\forall b\in \zo\colon \set{\vr, \Del{r}{\cS}} \cap \cA_b \neq \emptyset} > 1/q(\ell,\log\size{\Sigma}).
\end{align*}
\end{conjecture}


\paragraph{A weaker conjecture.}
\cref{thm:mainPR} can be proven based on the following conjecture that is  weaker  than  (\ie implied by ) \cref{conj:1}, and implied by the conjecture used in the informal discussion on  \cref{sec:Technique}. Since, however,  the following conjecture is somewhat  harder to work with, and since we know how to prove neither, we chose the base \cref{thm:mainPR}  on   \cref{conj:1} above.

\begin{notation}
	For $x\in \sel$,  $\cS \subseteq [\ell]$ and $\cT \in \cP([\ell])$, define  $x^{\cs,\cT} \subseteq \sbl$ by $
	x^{\cs,\cT}= \set{\Del{x}{\cS \cap \cS'}\colon \cS'\in \cT} 
	$.% Let $\Dels{x}{\cS} = \set{x} \cup \set{\Del{x}{\cS}}$.
\end{notation}

\begin{conjecture}\label{conj:3}
	For any $\sigma,\lambda, \mu>0$, there exists $q \in \poly$ such that the following holds.  Let $\cT$ be a  $q(\ell)$-size subset of $\cP([\ell])$, and let  $\Sigma$ be a finite alphabet and let $\cA_0,\cA_1 \subset \sbl$  be  two disjoint sets such that %for both $b\in \zo$:
	%\begin{align}\label{eq:1}
	%\ppr{\cS \gets {[n] \choose \sigma n}}{\ppr{r\gets \sel}{\Dels{r}{\cS} \subseteq \cA_b} \ge \delta} \ge \gamma
	%\end{align}
	
	\begin{align*}%\label{eq:1}
	\ppr{\cS \gets \bls}{\forall b\in \zo \colon \ppr{r\gets \sel}{  r^{\cs,\cT} \subseteq \cA_b} \ge \lambda} \ge \mu.
	\end{align*}
	
	Then,
	\begin{align*}%\label{eq:2}
	\ppr{\vr\gets \sel,\cS \gets \bls}{\forall b\in \zo\colon r^{\cs,\cT} \cap \cA_b \neq \emptyset} > 1/q(\ell,\log\size{\Sigma}).
	\end{align*}
\end{conjecture}
By letting $\cT = \set{\emptyset,[\ell]}$, we get \cref{conj:1}, and by letting $\cT = \set{\cs_1,\cs_2}$ for $\cs_1,\cs_2$ being an equal size partition of $[\ell]$, we get the conjecture from \cref{sec:Technique}.  
\remove{
The attack described in 
\subsection{Other Variants and Generalized Conjecture}
\Inote{need update}
 
\paragraph*{Variant with two aborting sets.} The following conjecture also suffices for our purposes (albeit for a slightly different attack). 
	
\begin{conjecture}\label{conj:2}
For any $\sigma,\lambda, \mu>0$, there exists $q \in \poly$ such that the following holds for large enough $\ell$.  Let  $\Sigma$ be a finite alphabet and let $\cA_0,\cA_1 \subset \sbl$  be  two disjoint sets such that %for both 

\begin{align*}%\label{eq:1}
\ppr{\cS_0,\cs_1 \gets {\binom{[\ell]}{\floor{\sigma \ell}}}}{\forall b\in \zo \colon \ppr{r\gets \sel}{\Del{r}{\cS_0},\Del{r}{\cS_1} \in \cA_b} \ge \lambda} \ge \mu.
\end{align*}
		
Then,
\begin{align*}%\label{eq:2}
\ppr{r\gets \sel,\cS_0,\cs_1\gets {\binom{[\ell]}{\ceil{\sigma \ell}}}}{\forall b\in \zo\colon \set{\Del{r}{\cS_0},\Del{r}{\cS_1}}  \cap \cA_b \neq \emptyset} > 1/q(\ell,\log\size{\Sigma}).
\end{align*}
\end{conjecture}



\Inote{motivate it}

\paragraph*{Variant for inefficient attack.}  The following conjecture, while not sufficient for our purposes, is implied by all of the above.


 


}